---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```
# Exceptional - Better exception handling for R

The goal of exceptional is to create better exception handling. This is achived
by:

* providing tools for creating not just error or warning messages at the point 
  where the exception occurs, but creating an objecto of class "exception" that
  contains the message that should be displayed ot the user, the nature of it 
  (e.g. error, warning, note etc.) and other elements that can be accessed later
  by the user.
* allowing the user to acces information about the exception that is beyond the 
  scope of a simple message `warning()` or `stop()` can deliver. Again, this is 
  possible through the class "exceptional".
  
## Example

This is a basic example:
```{r example}
library("exceptional")

```

Instead of 
```{r}
message("I am pretty urgent")
```

We could do 
```{r}
my_alert <- create_exception(
  "I am pretty urgent", 
  nature = "alert", 
  cause = "because the weather is getting bad. Look at the clouds",
  parameter = letters[1:3],
  id = create_id("mypackage", 1)
)

my_alert
my_alert$parameter
```

Exceptions should have a unique id composed of the package name and a number and
may be documented.

```{r}
my_alert$id
my_alert$cause
```
